\chapter*{}
%\thispagestyle{empty}
%\cleardoublepage

%\thispagestyle{empty}

\cleardoublepage
\thispagestyle{empty}

\begin{center}
% Title name
{\large\bfseries \myTitle}\\
\end{center}
\begin{center}
% Author name
\myName\\
\end{center}

%\vspace{0.7cm}
\noindent{\textbf{Keywords}: microservices, cloud, education.}\\

\vspace{0.7cm}
\noindent{\textbf{Abstract}}\\

This work is about the building of a simple  open source students management
web-based app but with technologies and a architecture opposite to the common.
This work is about the design a microservices based architecture that will be
able to grow, easily scalable, technology agnostic and with the enough decoupled
to be functionall separatelly. But above all, is an excuse to learn, research,
about programming, workteam manage, project structuration and planification.
\cleardoublepage

\thispagestyle{empty}

\noindent\rule[-1ex]{\textwidth}{2pt}\\[4.5ex]


Me, \textbf{Juan Antonio Fernández Sánchez}, Computer Science Degree student at
\textbf{Escuela Técnica Superior de Ingenierías Informática y de Telecomunicación},
ETSIIT, at \textbf{Granada University} with DNI 45601217Z, allow the emplacement of this a copy
of this work in the library of the center to be able to consult by anyone that desire.

\vspace{6cm}

\noindent Fdo: \myName

\vspace{2cm}

\begin{flushright}
\myDate % date of project deliver
\end{flushright}

\chapter*{}
\thispagestyle{empty}

\noindent\rule[-1ex]{\textwidth}{2pt}\\[4.5ex]

D. \textbf{\myMentor}, \myMentorStatus

\vspace{0.5cm}

\textbf{Informan:}

\vspace{0.5cm}

That present work, titled \textit{\textbf{\myTitle}},
has been realized under their supervision by \textbf{\myName}, and I authorize their defense front of the correspondent court.

\vspace{0.5cm}

And for the record, he dispatch and sign this report at \myDate.

\vspace{1cm}

\textbf{The mentor:}

\vspace{5cm}

\noindent \textbf{\myMentor}

\chapter*{Acknowledgements}
\thispagestyle{empty}

       \vspace{1cm}


This would not have been possible without all the support, patient and
encourage of my family. Thank you so much for all that you has given me and
I will be never able to give back.
\intro
Thanks to Juan Jose Ramos, mentor at Telefonica Talentum program, for all their
tips and all their help with business and technical approach, and of course to
all fellows of the program, now friends also, that I hope to match in future projects.
\intro
Sincere thanks of course to JJ Merelo, for their help, inspiration, for
the opportunity to meet cool people and overall, fot their patient with a student
like me.
\intro
And especially to \textit{Susana}. Thanks you for being always there.
