\chapter{Requirements}

In this chapter, we are going to describe which are the requirement that our system has.
It will be used User Stories\footnote{A user story is an informal, natural language
description of some features of a software system. See bibliography to know more.}
methodology which it will be talked a bit more in the next chapter.
This tool will be useful to identify the requirements of the system by a
human readable way., removing all possible layer between design and traditional
requisites specification process.
\intro
User stories can be very minimal (unit) and very general. That mean that we
can do a user story that is a simple requirement or a very general issue.
If the criteria to follow is to do very minimal users stories, we could be
hundred of them, so in this case, is better have an upper abstraction level
to have fewer user stories but with more content, at least when is the
first time that the team uses this methodology.

\section{Minimal user requirements}

The managers of the center can't have a precise idea about which must be the
functions of the software. They have a clear idea about what kind of process in
their daily work there are the heaviest and consume more paper, that is which
they want to digitalize, but they have not thought about navbars, icons, colors palettes,
user interfaces design or something like this.  They have abstract ideas that will
need dimensioning and shaping but which in synthesis offer the minimum system requirements.

\subsection{General needs}

these are the general requisites that customers have, independently of the logic of the application.
We are talking about software and it will need run in somewhere and must be cheap
and easy to run.
At first, there are not any pre-requirements. Maybe they prefer it can run in
devices like smartphones, tablets, laptops,
but they do not have a good technical knowledge and for they are indifferent that
it will be a native app, a web app or some strange artifact.
\intro
On the other hand, exists an essential requirement, must be run on any device for
the same person, independently of the machine where it be (sometimes in laptop
and others in a smartphone, for example).
\intro
User stories related: GN-1 to GN-3 on appendix A.


\subsection{Academic Management System}

As we can imagine, a center have a lot of differents kind of relationships,
and as an obligatory part of the system, it must be offered a simple way to manage this.
Teachers impart subjects to a group of students (called classes), students are
enrolled in subjects, and so on.
\intro
User stories related: AMS-1 to AMS-7 on appendix A.

\subsubsection{Attendance Controls}

This is one of most important process to digitalize, the amount of data that is saved on
paper make impossible to manage fluenty and much less  analyzing them.
They need a simple way, a simple interface to do this that allow they to save time
(doing it, analysis and management it), paper and effort.
\intro
User stories related: AC-1 on appendix A.

\subsection{Class Controls}

A part of manage of classrooms they must offers a say to follow the students
evolution in class, behaviour, positives and negativss and another lot of things
like paper save, time and effort as section above.
\intro
User stories related: CC-1 on appendix A.

\subsection{Marks}

As another process that more paper consumes is the marks management.
They want a system that simplify the process of insertion, analysis, and management.
Without any special idea in mind are open to any good user interface that simplifies it.
\intro
User stories related: MRKS-1 on appendix A.

\subsection{Disciplinary Notes}
It also must provide a management of this kind of notes, in which a bad behaviour
of a studnet is saved, managed and fully reported to the specific users inside of
app, as tutors, pedagogue, etc, for example.
\intro
User stories related: DN-1 to DN-2 on appendix A.

\subsection{Simple and advance reports}

Another part interesting for they is improve the reports that they obtains from
their data. The on paper support do this almost imposible to big scale, an a
important feature must be do this posible. Advanced reports about a lot of kind
of items, like students, state of subjects, marks, etc, in seconds with some cliks.
This will improve the take of decisions and will do better meetings with better
decisions based on good and crontastable data.
\intro
User stories related: SAR-1 on appendix A.

\subsection{Autonomic Official System Connection}

The national system of education in which this center is framed have a diferents
informatic reginal system. In this case, in Andalucia, where the certer is it called
SENECA (other in other places of the country). All public and semipublic educaitonal
centers need save data in this systems necessarily, and this haven't a simple public
API where connet us. They must be done dirty way, making a maxed mode way to simplify
the download and download of data that minify the interaction with the official system.
\intro
User stories related: SNC-1 on appendix A.

\section{Minimal system requirements}

The system, as if it was another user has their own requisites,
and can be handled as normal user stories.
So, with the architecture that we are talking about all parts of the system
(the microservices) must be independent and low coupled also must be able to run
in diferents places using always the same communication protocol (API Rest in this case).
These are not a lot of requisites but are indispensable to the system has the properties
that we expected.
\intro
User stories related: MSR-1 and MSR-2 on appendix A.
